A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-05 tex/codatadp.tex
more

\cheat
\item
\emph{It must be possible to express cyclic values as closed terms and
to enumerate them.} For finite model finding, requires a $\mu$ notation,
e.g., $\const{SCons}(3,\, \mu s.\; \const{SCons}(1,\, \const{SCons}(4,\, s)))$
represents the lasso-shaped sequence $3, 1, 4, 1, 4, \ldots$\kern0.1em. %%% TYPESETTING: kern
\end{itemize}

@@

The procedure is implemented in the SMT solver CVC4 as rewriting and a theory solver
(Section~\ref{sec:the-theory-solver}). It implements a precise strategy for applying
inferences. It consists of about 2000 lines of \cpp{} code, among which 1600 are
shared between datatypes and codatatypes. The code is integrated in the
development version of the solver and is expected to be part of the 1.5 release.
%
The decision procedure is evaluated on %hand-crafted examples and on
problems generated from Isabelle theories using Isabelle's Sledgehammer tool
(Section~\ref{sec:experimental-results}).

>>>>

\cheat
\item
\emph{It must be possible to express cyclic values as closed terms and
to enumerate them.} This is necessary both for finite model finding (modulo theories)
and for theory combinations. The $\mu$ notation is used to represent cyclic ($\omega$-regular)
values. For example,
$\const{SCons}(3,\, \mu s.\; \const{SCons}(1,\, \const{SCons}(4,\, s)))$
represents the lasso-shaped sequence $3, 1, 4, 1, 4, \ldots$\kern0.1em. %%% TYPESETTING: kern
\end{itemize}

@@

The procedure is implemented in the SMT solver CVC4 as rewriting and a theory solver
(Section~\ref{sec:the-theory-solver}).
It consists of about 2000 lines of \cpp{} code, among which 1600 are
shared between datatypes and codatatypes. The code is integrated in the
development version of the solver and is expected to be part of the 1.5 release.
%
An evaluation on %hand-crafted examples and on
problems generated from Isabelle theories using Isabelle's Sledgehammer tool
demonstrates the usefulness of the approach (Section~\ref{sec:experimental-results}).
